Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-09-27 paper/paper.tex

>>>>

At the university of Augsburg, programming courses for students of physics and
materials science are offered since about ten years. During that time, the
exercises mentioned in \label{sec:nbgrader} have been gradually developed and
tested in exercise sessions organized in groups of two or three students under
guidance of teaching personnel. This format was also be used to develop the
Jupyter notebooks. The close interaction between students and teachers allowed
to analyze the way students make use of the notebooks and to identify problems
in the tests used to do the grading and to improve these tests. While the courses
so far had about 10-20 students, we expect to have of the order of 100 students
from next year on. Then, the experience collected with \texttt{nbgrader} will
be very valuable.

In the lectures on programming, Jupyter notebook have succesfully been used for
several years for teaching. In addition, students were encouraged to use them
during the lectures on their laptop but were found to rarely make use of this
opportunity. They mostly preferred to attentively follow the lecture. However,
Jupyter notebooks were offered to students for download so that they could
work on them at home. It is not clear, how much use was made of this possibility.
On the other hand, in the regular physics courses, Jupyter notebooks have been
rarely used and probably will not be used for an entire course. However, we
expect to use Jupyter notebooks more often for demonstration purposes where
appropriate.
